APPM 3310 Project\\\Large{Static Analysis of Truss Systems}

### 2016-04-26 paper.tex
Add Conclusion from Ryan Marizza.

>>>>

The truss analyzer is able to properly analyze a complex truss system based on
three known values: forces, displacements, and elastic moduli using
calculations based on these values and structure geometry. The analysis is
able to break down a truss system and implement the DSM by idealizing the
truss system, and simplifying complex real world phenomena into a manageable
set of linear stiffness equations. These stiffness equations are used to
describe the structure's elements, each of which can be subjected to an
external force/displacement at a node. From this, a global stiffness matrix is
produced and solved using the force vectors and displacement vectors. This DSM
truss analysis can be used for complex structures and is useful when it comes
to structures with many distinct nodes, each with distinct forces and
displacements. Solving for the stresses on these nodes without the use of
linear algebra is nearly impossible. Through this DSM analysis, using linear
algebraic methods, important engineering structures, notably: bridges, wings,
buildings, can be analyzed. Knowing the stresses on elements of these
structures allows engineers to predict behavior of structures under force.
Such behaviors that can be predicted are elastic deformation, plastic
deformation, crack growth, crack propagation, and structural failure. From
this it is easy to see why such structure analysis is important.
